Multiproduct Batch Processing Time Maximization Problem

### 2023-07-03 (2023) Fraga et al.tex
updating files

\documentclass[preprint,12pt,authoryear]{elsarticle}

@@

%%Graphical abstract
\begin{graphicalabstract}
%\includegraphics{grabs}
\end{graphicalabstract}

@@

@@

\begin{equation}
max \quad T
\end{equation}

\begin{equation}
P_i - \textrm{p}_i * T  = 0 \quad \forall i
\end{equation}

\begin{equation}
P_i - D_i - O_i - I_i = 0 \quad \forall i
\end{equation}

\begin{equation}
O_i \leq \textrm{UO}_i \quad \forall i
\end{equation}

\begin{equation}
I_i \leq \textrm{UI}_i \quad \forall i
\end{equation}

\begin{equation}
T \leq \textrm{Z}
\end{equation}

\begin{equation}
D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
\end{equation}

@@

So the solution method can be decomposed into 4 steps: \\

step 1: find $T'$, where:

\begin{equation}
T' = \lfloor{\min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}}\rfloor
\end{equation}

step 2: calculate $S_i$ for all products.

\begin{equation}
\label{eq:unmet}
S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
\end{equation}

step 3: find $T''$, where:

\begin{equation}
T'' = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}}\rfloor
\end{equation}

step 4: calculate $T$, where:

\begin{equation}
T = \min \{T , \textrm{Z}\}
\end{equation}

@@

\begin{table}[h]
\begin{center}
\begin{footnotesize}
\begin{tabular}[c]{l r r r r}
problem & LINGO solver & time (s) & analytical method & time (s) \\
\cline {1-5} \\
MBPTMP 1 & 55 & 0 & 55 & 0.001 \\
MBPTMP 2 & 48 & 0.06 & 48 & 0.001 \\
MBPTMP 3 & & & 30 & 0.001 \\
RMBPTMP 20 & & & 100 & 0.001 \\
RMBPTMP 50 & & & 98 & 0.001\\
RMBPTMP 100 & & & 98 & 0.002\\
RMBPTMP 1,000 & & & 78 & 0.002\\
RMBPTMP 10,000 & & & 70 & 0.006 \\
\cline {1-5} \\
\end{tabular}
\label{tab:results}
\caption{Results obtained with the LINGO solver and the analytical method}
\end{footnotesize}
\end{center}
\end{table}

>>>>

\documentclass[review,12p]{elsarticle}

%% The `ecrc' package must be called to make the CRC functionality available
%\usepackage{ecrc}

@@

%%Graphical abstract
\begin{graphicalabstract}
\includegraphics[width=13cm]{graphical.png}
\end{graphicalabstract}

@@

a\\
a\\
a\\
a\\
a\\
a\\
a\\

@@

\begin{equation}
max \quad T
\end{equation}
$\qquad \qquad \qquad \qquad \qquad \qquad s.t.$ \\
\begin{equation}
P_i - \textrm{p}_i * T  = 0 \quad \forall i
\end{equation}
\begin{equation}
P_i - D_i - O_i - I_i = 0 \quad \forall i
\end{equation}
\begin{equation}
D_i \leq \textrm{UD}_i \quad \forall i
\end{equation}
\begin{equation}
O_i \leq \textrm{UO}_i \quad \forall i
\end{equation}
\begin{equation}
\sum_i{O_i} \leq \textrm{O}
\end{equation}
\begin{equation}
I_i \leq \textrm{UI}_i \quad \forall i
\end{equation}
\begin{equation}
\sum_i{I_i} \leq \textrm{I}
\end{equation}
\begin{equation}
T \leq \textrm{Z}
\end{equation}
\begin{equation}
T, D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
\end{equation}

@@

a\\
a\\
a\\
a\\
a\\
a\\
a\\
a\\
a\\
a\\
a\\
a\\
a\\

The analytical method can be decomposed into 4 steps: \\

step 1: find $T'$, where:
\begin{equation}
T' = \lfloor{\min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}}\rfloor
\end{equation}

step 2: calculate $S_i$ for all products.
\begin{equation}
\label{eq:unmet}
S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
\end{equation}

step 3: find $T''$, where:
\begin{equation}
T'' = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}}\rfloor
\end{equation}

step 4: calculate $T$, where: 
\begin{equation}
T = T' + T''
\end{equation}
\begin{equation}
T = \min \{T , \textrm{Z}\}
\end{equation}

@@

\begin{table}[h]
\begin{center}
\begin{footnotesize}
\begin{tabular}[c]{l r r r r}
problem & LINGO solver & time (s) & analytical method & time (s) \\
\cline {1-5} \\
MBPTMP 1 & 55 & 0 & 55 & 0.001 \\
MBPTMP 2 & 48 & 0.06 & 48 & 0.001 \\
MBPTMP 3 & & & 30 & 0.001 \\
RMBPTMP 20 & 100 & 0.08 & 100 & 0.001 \\
RMBPTMP 50 & 98 & 0.12 & 98 & 0.001\\
RMBPTMP 100 & 98 & 0.12 & 98 & 0.002\\
RMBPTMP 1,000 & 78 & 3.10 & 78 & 0.002\\
RMBPTMP 10,000 & 70 & 168.87 & 70 & 0.006 \\
\cline {1-5} \\
\end{tabular}
\label{tab:results}
\caption{Results obtained with the LINGO solver and the analytical method}
\end{footnotesize}
\end{center}
\end{table}
